### 2023-01-11 paper.Rmd
word count
added function declarations to chunk with example
added info on devel version of papaja

keywords          : "Anticlustering, k-means, k-plus, variance, covariance, skewness, kurtosis, stimulus selection"
wordcount         : "4972"

@@

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
# for formatting numbers in Rmarkdown, use my package prmisc (https://github.com/m-Py/prmisc)
library("prmisc") # remotes::install_github("m-Py/prmisc") 
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

@@

@@

The simulation was implemented using the statistical programming language R [Version 4.2, @R-base]. The R package `anticlust` [Version 0.6.1, @R-anticlust; @papenberg2020] was used to optimize the anticlustering objectives. The R package `faux` [Version 1.1.0, @R-faux] was used to generate the multivariate normal data sets that were processed during the simulation. The R packages `dplyr` [Version 1.0.7, @R-dplyr], `ggplot2` [Version 3.3.5, @R-ggplot2], `papaja` [Version 0.1.0.9997, @R-papaja], `tidyr` [Version 1.1.3, @R-tidyr] and `DescTools` [Version 0.99.45, @R-desctools] were used for data analysis and result presentation. The simulation study is fully reproducible via code and data that is accessible from the accompanying OSF repository (**link TODO**).

>>>>

keywords          : "Anticlustering, k-means, k-plus, variance, covariance, skewness, kurtosis, stimulus selection"
wordcount         : "5114"

@@

```{r setup, include = FALSE}
library("papaja") # use the development version: `remotes::install_github("crsh/papaja@devel")`; currently 0.1.1.9001
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
# for formatting numbers in Rmarkdown, use my package prmisc (https://github.com/m-Py/prmisc)
library("prmisc") # remotes::install_github("m-Py/prmisc") 
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

@@

```{r motivatingExample}

@@

The simulation was implemented using the statistical programming language R [Version 4.2, @R-base]. The R package `anticlust` [Version 0.6.1, @R-anticlust; @papenberg2020] was used to optimize the anticlustering objectives. The R package `faux` [Version 1.1.0, @R-faux] was used to generate the multivariate normal data sets that were processed during the simulation. The R packages `dplyr` [Version 1.0.7, @R-dplyr], `ggplot2` [Version 3.3.5, @R-ggplot2], `papaja` [Version 0.1.1.9001, @R-papaja], `tidyr` [Version 1.1.3, @R-tidyr] and `DescTools` [Version 0.99.45, @R-desctools] were used for data analysis and result presentation. The simulation study is fully reproducible via code and data that is accessible from the accompanying OSF repository (**link TODO**).
